This is the title : v\versionnumber

### 2017-11-24 templates/livecoms-template-reviews.tex
Add templates for all other document types, as well as a sample document. Update READMEs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% LIVECOMS ARTICLE TEMPLATE FOR BEST PRACTICES GUIDE
%%% ADAPTED FROM ELIFE ARTICLE TEMPLATE (8/10/2017)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PREAMBLE
\documentclass[9pt,lessons]{livecoms}
% Use the 'onehalfspacing' option for 1.5 line spacing
% Use the 'doublespacing' option for 2.0 line spacing
% Use the 'lineno' option for adding line numbers.
% The 'bestpractices' option for indicates that this is a best practices guide.
% Omit the bestpractices option to remove the marking as a LiveCoMS paper.
% Please note that these options may affect formatting.

@@

\begin{abstract}
This particular document provides a skeleton illustrating key sections for a Lessons Learned document.
Please see the sample \texttt{sample-document.tex} in \url{github.com/livecomsjournal/article_templates/templates} for additional information on and examples of using the LiveCoMS LaTeX class.
Here we also assume familiarity with LaTeX and knowledge of how to include figures, tables, etc.; if you want examples, see the sample just referenced.

@@

Here you would explain what problem you are tackling and briefly motivate your work.
Since a Lessons Learned document provides negative results in a particular category, you will want to clearly define your category and also motivate the application of your work to your particular problem.

We suggest that you envision your document potentially extending in the future to include other Lessons Learned in the same category, so you may want to organize your work in a way which would allow this type of extension (e.g. providing a general introduction then using subsections to explain your particular problem) -- for example, describing potential of mean force calculations generally, then in a subsection motivating your particular application of them.

In this particular template, we have removed most of the usage examples which occur in \texttt{sample-document.tex} to provide a minimal template you can modify; however, we retain a couple of examples illustrating more unusual features of our templates/article class, such as the checklists, and information on algorithms and pseudocode.

A Lessons Learned document is a regular scientific article, and should be prepared with similar organization.
Sample typical section headers follow.

\section{Theory and Methods}

You should use a section (or separate sections, if this yields better organization) to describe the theory and methods relevant to your work.

This should include all information required for a reader to reproduce the results, including software version numbers and links to any in-house files or scripts

\section{Results}

You would give your results here.
Since the goal here is not just to present negative results, but also to provide lessons learned from doing so, you will want to make sure you have data to show why your approach failed.

\section{Discussion}

Discussion should highlight the lessons learned and give tips for avoiding future mistakes.
Try to tell readers what you wish you had known before starting.

@@

Give conclusions.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% LIVECOMS ARTICLE TEMPLATE FOR BEST PRACTICES GUIDE
%%% ADAPTED FROM ELIFE ARTICLE TEMPLATE (8/10/2017)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PREAMBLE
\documentclass[9pt,review]{livecoms}
% Use the 'onehalfspacing' option for 1.5 line spacing
% Use the 'doublespacing' option for 2.0 line spacing
% Use the 'lineno' option for adding line numbers.
% The 'bestpractices' option for indicates that this is a best practices guide.
% Omit the bestpractices option to remove the marking as a LiveCoMS paper.
% Please note that these options may affect formatting.

@@

\begin{abstract}
This particular document provides a skeleton illustrating key sections for a Perpetual Review document.
Please see the sample \texttt{sample-document.tex} in \url{github.com/livecomsjournal/article_templates/templates} for additional information on and examples of using the LiveCoMS LaTeX class.
Here we also assume familiarity with LaTeX and knowledge of how to include figures, tables, etc.; if you want examples, see the sample just referenced.

@@

Here you would explain what area you are reviewing, and motivate your review.

In this particular template, we have removed most of the usage examples which occur in \texttt{sample-document.tex} to provide a minimal template you can modify.

\section{Review organization}

In general the organization of your review is up to you.
LiveCoMS reviews are similar to traditional reviews except that they are updatable.

\subsection{Perpetual review}

You will probably want to devote at least a small amount of space explaining to your readers what a Perpetual Review is and highlighting how they can get involved via your git issue tracker or by communicating with you directly.
In contrast to a traditional review, here it \emph{will} help you if the community points out other, related work that perhaps should be cited, since it reduces the need for you to dig deeply into the literature to keep your work up to date.

Tutorials should endeavor to cover the specific task at hand, and also highlight how the steps might need to be modified (or additional care might need to be taken at particular points) to handle more general cases.

The scope of the tutorial, as well as the expected proficiencies / outcomes for researchers who complete the tutorial, should be clearly defined.
This will often happen in a specific section or subsection in the article itself.

\section{Prerequisites}

In keeping with other types of articles at LiveCoMS, it may be useful (at your discretion) to note any prerequisites your article assumes and who it is targeted at.

@@

It's appropriate to wrap up with discussion and conclusions.
